Timeliness of security updates for Android

### 2014-11-14 dastats.tex
Updated dastats with better display of uncertainties

\newcommand{\daNumManufacturers}{260}
\newcommand{\daNumSigManufacturers}{8}

@@

\newcommand{\daOSTotalDaysData}{1\,130\,000}
\newcommand{\daMeanInsecurityPerc}{$87.2 \pm 0.0342\%$}

@@

\newcommand{\daUpdatedness}{$0.0561 \pm 0.000258$}
\newcommand{\daSecurityScore}{$2.75 \pm 0.00157$}

@@

\newcommand{\daNumFullVersionUpdates}{4\,210}

@@

\newcommand{\daNumFullOnlyVersionUpdates}{637}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline LG & $0.12 \pm 0.00$ & $0.32 \pm 0.00$ & 0.74 & $3.38 \pm 0.01$ \\  Motorola & $0.16 \pm 0.00$ & $0.13 \pm 0.00$ & 0.77 & $2.94 \pm 0.01$ \\  other & $0.13 \pm 0.00$ & $0.06 \pm 0.00$ & 0.64 & $2.75 \pm 0.00$ \\  Samsung & $0.14 \pm 0.00$ & $0.05 \pm 0.00$ & 0.71 & $2.67 \pm 0.00$ \\  Sony & $0.13 \pm 0.00$ & $0.18 \pm 0.00$ & 1.02 & $2.64 \pm 0.01$ \\  HTC & $0.14 \pm 0.00$ & $0.09 \pm 0.00$ & 0.89 & $2.55 \pm 0.00$ \\  asus & $0.16 \pm 0.00$ & $0.56 \pm 0.01$ & 6.06 & $2.31 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & 4.91 & $0.18 \pm 0.00$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table}}
\newcommand{\daTabSecScoresmodel}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.54 \pm 0.00$ & $0.53 \pm 0.01$ & 1.53 & $4.80 \pm 0.03$ \\  Nexus 4 & $0.23 \pm 0.00$ & $0.82 \pm 0.01$ & 6.06 & $3.39 \pm 0.04$ \\  Nexus 7 & $0.19 \pm 0.00$ & $0.74 \pm 0.01$ & 5.92 & $3.02 \pm 0.04$ \\  other & $0.13 \pm 0.00$ & $0.12 \pm 0.00$ & 0.64 & $2.94 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & 0.39 & $2.91 \pm 0.02$ \\  HTC Sensation & $0.36 \pm 0.00$ & $0.01 \pm 0.01$ & 1.59 & $2.47 \pm 0.02$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & 1.20 & $2.33 \pm 0.01$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & 1.00 & $1.75 \pm 0.01$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & 2.52 & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & 1.73 & $0.94 \pm 0.02$ \\  GT-I9300 & $0.15 \pm 0.00$ & $0.01 \pm 0.00$ & 6.17 & $0.64 \pm 0.01$ \\  GT-I9505 & $0.00 \pm 0.00$ & $0.18 \pm 0.00$ & 6.83 & $0.56 \pm 0.01$ \\  GT-N7100 & $0.07 \pm 0.00$ & $0.00 \pm 0.01$ & 6.91 & $0.28 \pm 0.02$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & 3.05 & $0.27 \pm 0.02$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table}}
\newcommand{\daTabSecScoressummary}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline nexus & $0.36 \pm 0.00$ & $0.52 \pm 0.00$ & 0.68 & $5.02 \pm 0.01$ \\  notnexus & $0.12 \pm 0.00$ & $0.04 \pm 0.00$ & 0.64 & $2.68 \pm 0.00$ \\ \end{tabular} \caption{Security scores for summaries} \label{tab:sec_summary} \end{table}}
\newcommand{\daUpdatednessPerc}{$5.61 \pm 0.0258\%$}
\newcommand{\daNumOSDevices}{18\,900}

@@

\newcommand{\daSecScoreWorstmanufacturer}{Symphony}

@@

\newcommand{\daSecScoreBestmanufacturerScore}{$3.38 \pm 0.011$}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.175 \pm 0.00428$}
\newcommand{\daSecScoreBestmodelScore}{$4.8 \pm 0.0254$}
\newcommand{\daSecScoreWorstmodelScore}{$0.274 \pm 0.0209$}

@@

\newcommand{\daVulnFree}{$0.128 \pm 0.000342$}

@@

\newcommand{\daNumUpdatesUpgrades}{3\,320}

@@

\newcommand{\daEndDate}{2014-11-05}

@@

\newcommand{\daTabSecScoresoperator}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.25 \pm 0.00$ & $0.12 \pm 0.00$ & 0.37 & $3.79 \pm 0.01$ \\  T-Mobile & $0.19 \pm 0.00$ & $0.18 \pm 0.00$ & 0.48 & $3.57 \pm 0.01$ \\  Orange & $0.21 \pm 0.00$ & $0.09 \pm 0.00$ & 0.39 & $3.52 \pm 0.02$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & 0.44 & $3.41 \pm 0.01$ \\  3 & $0.15 \pm 0.00$ & $0.09 \pm 0.00$ & 0.49 & $3.15 \pm 0.01$ \\  AT\&T & $0.12 \pm 0.00$ & $0.08 \pm 0.00$ & 0.43 & $3.08 \pm 0.01$ \\  Vodafone uk & $0.13 \pm 0.00$ & $0.10 \pm 0.00$ & 0.52 & $3.07 \pm 0.01$ \\  Verizon & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & 0.81 & $2.82 \pm 0.01$ \\  unknown & $0.10 \pm 0.00$ & $0.22 \pm 0.00$ & 1.08 & $2.57 \pm 0.01$ \\  n Telenor & $0.03 \pm 0.00$ & $0.10 \pm 0.00$ & 1.42 & $1.58 \pm 0.01$ \\  Airtel & $0.07 \pm 0.00$ & $0.03 \pm 0.00$ & 1.96 & $1.08 \pm 0.01$ \\  Grameenphone & $0.01 \pm 0.00$ & $0.01 \pm 0.00$ & 2.04 & $0.76 \pm 0.00$ \\  Robi & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & 2.23 & $0.70 \pm 0.01$ \\  banglalink & $0.00 \pm 0.00$ & $0.03 \pm 0.00$ & 2.95 & $0.39 \pm 0.00$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table}}

@@

\newcommand{\daSecScoreBestoperatorScore}{$3.79 \pm 0.0128$}

@@

\newcommand{\daSecScoreWorstoperatorScore}{$0.386 \pm 0.0049$}

@@

\newcommand{\daSecScoreWorstmanufacturerNumFullVersions}{14}

@@

\newcommand{\daSecScoreWorstoperatorNumFullVersions}{58}

@@

\newcommand{\daOSCurveFitParamFirst}{87.4}

@@

\newcommand{\daOSCurveHalfDeployed}{$308 \pm 81.8$}
\newcommand{\daOSCurveFullDeployed}{$1\,040 \pm 235\,000$}

@@

\newcommand{\daAPICurveHalfDeployed}{$330 \pm 84.0$}

@@

\newcommand{\daUpdatesPerYear}{$1.35 \pm 0.0209$}

@@

\newcommand{\daMeanInsecurityPercNominal}{8\,720\%}
\newcommand{\daVulnFreeNominal}{0.128}
\newcommand{\daUpdatednessNominal}{0.0561}
\newcommand{\daUpdatednessPercNominal}{561\%}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.386}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.175}
\newcommand{\daUpdatesPerMonthPerVersion}{3.61}

>>>>

\newcommand{\daNumManufacturers}{261}
\newcommand{\daNumSigManufacturers}{9}

@@

\newcommand{\daOSTotalDaysData}{1\,140\,000}
\newcommand{\daMeanInsecurityPerc}{$87.3 \pm 0.0\%$}

@@

\newcommand{\daUpdatedness}{$0.0558 \pm 0.0002$}
\newcommand{\daSecurityScore}{$2.75 \pm 0.00$}

@@

\newcommand{\daNumFullVersionUpdates}{4\,220}

@@

\newcommand{\daNumFullOnlyVersionUpdates}{640}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline LG & $0.12 \pm 0.00$ & $0.32 \pm 0.00$ & 0.74 & $3.38 \pm 0.01$ \\  Motorola & $0.16 \pm 0.00$ & $0.13 \pm 0.00$ & 0.77 & $2.93 \pm 0.01$ \\  other & $0.13 \pm 0.00$ & $0.06 \pm 0.00$ & 0.64 & $2.75 \pm 0.00$ \\  Samsung & $0.14 \pm 0.00$ & $0.05 \pm 0.00$ & 0.71 & $2.67 \pm 0.00$ \\  Sony & $0.13 \pm 0.00$ & $0.18 \pm 0.00$ & 1.02 & $2.64 \pm 0.01$ \\  HTC & $0.14 \pm 0.00$ & $0.09 \pm 0.00$ & 0.89 & $2.55 \pm 0.00$ \\  asus & $0.15 \pm 0.00$ & $0.56 \pm 0.01$ & 6.06 & $2.30 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & 4.79 & $0.19 \pm 0.00$ \\  walton & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & 5.79 & $0.14 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table}}
\newcommand{\daTabSecScoresmodel}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.53 \pm 0.00$ & $0.53 \pm 0.01$ & 1.53 & $4.80 \pm 0.03$ \\  Nexus 4 & $0.23 \pm 0.00$ & $0.82 \pm 0.01$ & 6.06 & $3.39 \pm 0.04$ \\  Nexus 7 & $0.19 \pm 0.00$ & $0.74 \pm 0.01$ & 5.92 & $3.02 \pm 0.04$ \\  other & $0.13 \pm 0.00$ & $0.12 \pm 0.00$ & 0.64 & $2.94 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & 0.39 & $2.91 \pm 0.02$ \\  HTC Sensation & $0.36 \pm 0.00$ & $0.01 \pm 0.01$ & 1.59 & $2.47 \pm 0.02$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & 1.20 & $2.33 \pm 0.01$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & 1.00 & $1.75 \pm 0.01$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & 2.52 & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & 1.73 & $0.94 \pm 0.02$ \\  GT-I9300 & $0.15 \pm 0.00$ & $0.01 \pm 0.00$ & 6.15 & $0.64 \pm 0.01$ \\  GT-I9505 & $0.00 \pm 0.00$ & $0.18 \pm 0.00$ & 6.77 & $0.55 \pm 0.01$ \\  GT-N7100 & $0.07 \pm 0.00$ & $0.00 \pm 0.01$ & 6.91 & $0.28 \pm 0.02$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & 3.05 & $0.27 \pm 0.02$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table}}
\newcommand{\daTabSecScoressummary}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline nexus & $0.36 \pm 0.00$ & $0.51 \pm 0.00$ & 0.68 & $5.01 \pm 0.01$ \\  notnexus & $0.12 \pm 0.00$ & $0.04 \pm 0.00$ & 0.64 & $2.67 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table}}
\newcommand{\daUpdatednessPerc}{$5.58 \pm 0.02\%$}
\newcommand{\daNumOSDevices}{19\,000}

@@

\newcommand{\daSecScoreWorstmanufacturer}{walton}

@@

\newcommand{\daSecScoreBestmanufacturerScore}{$3.38 \pm 0.01$}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.139 \pm 0.006$}
\newcommand{\daSecScoreBestmodelScore}{$4.8 \pm 0.0$}
\newcommand{\daSecScoreWorstmodelScore}{$0.274 \pm 0.020$}

@@

\newcommand{\daVulnFree}{$0.127 \pm 0.000$}

@@

\newcommand{\daNumUpdatesUpgrades}{3\,330}

@@

\newcommand{\daEndDate}{2014-11-07}

@@

\newcommand{\daTabSecScoresoperator}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{Security score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.25 \pm 0.00$ & $0.12 \pm 0.00$ & 0.37 & $3.79 \pm 0.01$ \\  T-Mobile & $0.19 \pm 0.00$ & $0.18 \pm 0.00$ & 0.48 & $3.57 \pm 0.01$ \\  Orange & $0.21 \pm 0.00$ & $0.09 \pm 0.00$ & 0.39 & $3.52 \pm 0.02$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & 0.44 & $3.41 \pm 0.01$ \\  3 & $0.15 \pm 0.00$ & $0.09 \pm 0.00$ & 0.49 & $3.15 \pm 0.01$ \\  AT\&T & $0.12 \pm 0.00$ & $0.08 \pm 0.00$ & 0.43 & $3.08 \pm 0.01$ \\  Vodafone uk & $0.13 \pm 0.00$ & $0.10 \pm 0.00$ & 0.52 & $3.07 \pm 0.01$ \\  Verizon & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & 0.81 & $2.82 \pm 0.01$ \\  unknown & $0.10 \pm 0.00$ & $0.22 \pm 0.00$ & 1.08 & $2.57 \pm 0.01$ \\  n Telenor & $0.03 \pm 0.00$ & $0.10 \pm 0.00$ & 1.42 & $1.59 \pm 0.01$ \\  Airtel & $0.06 \pm 0.00$ & $0.03 \pm 0.00$ & 1.93 & $1.10 \pm 0.01$ \\  Grameenphone & $0.01 \pm 0.00$ & $0.02 \pm 0.00$ & 1.99 & $0.80 \pm 0.00$ \\  Robi & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & 2.19 & $0.73 \pm 0.01$ \\  banglalink & $0.00 \pm 0.00$ & $0.03 \pm 0.00$ & 2.90 & $0.40 \pm 0.00$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table}}

@@

\newcommand{\daSecScoreBestoperatorScore}{$3.79 \pm 0.01$}

@@

\newcommand{\daSecScoreWorstoperatorScore}{$0.4 \pm 0.0$}

@@

\newcommand{\daSecScoreWorstmanufacturerNumFullVersions}{20}

@@

\newcommand{\daSecScoreWorstoperatorNumFullVersions}{59}

@@

\newcommand{\daOSCurveFitParamFirst}{87.5}

@@

\newcommand{\daOSCurveHalfDeployed}{$308 \pm 81$}
\newcommand{\daOSCurveFullDeployed}{$1\,040 \pm 236\,000$}

@@

\newcommand{\daAPICurveHalfDeployed}{$330 \pm 84$}

@@

\newcommand{\daUpdatesPerYear}{$1.35 \pm 0.02$}

@@

\newcommand{\daMeanInsecurityPercNominal}{87.3\%}
\newcommand{\daVulnFreeNominal}{0.127}
\newcommand{\daUpdatednessNominal}{0.0558}
\newcommand{\daUpdatednessPercNominal}{5.58\%}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.4}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.139}
\newcommand{\daUpdatesPerMonthPerVersion}{3.62}
\newcommand{\daNumUpdateFullOnly}{0}
